Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-20 latex/comp_or.tex
Paper 2 update

\begin{algorithm}[H]
	\caption{$ACLP+RPDP (scenario,volume)$}  \label{alg:main}
	\begin{algorithmic}[1]
		\State Let $L, M, C$ be according to $scenario$ \label{main:LMC}
		\State $N \gets ItemsGeneration(scenario,volume)$ \label{main:items}
		\For {each $method$}
			\For {each $\pi \in S_K$} \label{main:loop1}
				\State $f_{\pi} \gets SolveTour(\pi, L, M, C, N, method )$ \label{main:method}
			\EndFor \label{main:loop2}
			\State $answer[scenario,volume,method] \gets \max f$ \label{main:f}
		\EndFor
		\State $ {\bf return}\ answer$
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{$SolveTour(\pi, L, M, C, N, method)$}  \label{alg:tour}

@@

		\State $\pi(0) \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q_{\pi(k)}, E^Q_{\pi(k)}, M \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M \cup N_{\pi(k)} \cup Q_{\pi(k)}, E^Q_{\pi(k)})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M \gets SetPalletsDestination( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1)$ \label{tour:node}
			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_2)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\State $ {\bf return}\ score / cost$ \label{tour:f}

@@

	\caption{ $SolveNode(mpACO, k, G)$ } \label{alg:aco}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$
		\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets Greedy(k, G, 1)$  \label{aco:greedy}
		\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^*(V_k,E^{N*}_k \cup E^Q_k)$
		\State $A \gets$ a number of ants or parallel processes to be determined for each iteration \label{aco:ants}
		\State $ga^k_{ij}   \gets 0$, $1 \leq i \leq m$, $1 \leq j \leq n_k$  \label{aco:init1}
		\State $\tau^k_{ij} \gets 1$, $1 \leq i \leq m$, $1 \leq j \leq n_k$   \label{aco:init2}
		\State $\alpha    \gets 1.0$ \label{aco:alpha}
		\State $\beta     \gets 4.0$ \label{aco:beta}
		\State $\rho      \gets 0.2$ \label{aco:rho}
		\State $stagnant \gets 0$
		\While{($stagnant < 3$) {\bf and} ($runtime < 0.7s$)} \label{aco:while}

@@

Figure \ref{fig:whip} represents the $n_k$\/ possible edges $e_{ij}^k$\/ of $p_i$\/ sorted by $\theta_{ij}^k$. \emph{Shims}\/ starts with a greedy solution, stopping at the edge with index $\eta_1[i]$ close to the local optimum (first phase). Then, considering even the edge with the index $\eta_2[i]$, it elaborates different possible complements for this pallet (second phase) and selects the best of these complements (third phase).

%Examples:
%$\to$ for a small problem if limit is 0.85 for the first phase of the solution process, remains 0.15 for second and third phases.
%$\to$ for a big problem if it is 0.98 for the first phase, it is 0.02 for the remaining phases.

\begin{algorithm}[H]
	\caption{ $SolveNode(Shims, k, G)$}  \label{alg:shims}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$
		\State Sort $M$ by $|p_i.d|$ in non-descending order \label{shims:pallets}
		\State $E^N_k \gets \varnothing$ 
		\State Let $E[1..m][1..n_k]$, where $E[i]$ is an array with $n_k$ edges $(p_i,t^k_j)$ sorted by $\theta_{ij}^k$ in non-ascending order, $1 \leq i \leq m$ \label{shims:edges}
		\State $gap \gets 2000/n_k*m$ \label{shims:gap} 
		\For{$i \gets 1$ to $m$} 
			\State $pv[i] \gets 0$		\label{shims:phase1a}
			\State $\eta_1[i] \gets 0$
			\While{($p_i.v - pv[i] > gap*p_i.v$) {\bf and} ($\eta_1[i]<n_k$)} \label{shims1:slack}
				\State $\eta_1[i] \gets \eta_1[i] + 1$ \label{shims:eta1}
				\State $e^k_{ij} \gets E[i][\eta_1[i]]$
				\If{($e^k_{ij}$ is feasible) {\bf and} ($t^k_j.v \leq p_i.v - pv[i]$)} 
					\State $E^N_k \gets E^N_k \cup \{e^k_{ij}\}$
					\State $pv[i] \gets pv[i] + t^k_j.v$ 
				\EndIf
			\EndWhile 
			\State $slack[i] \gets p_i.v - pv[i]$
			\State $\eta_2[i] \gets \eta_1[i]$
			\Repeat
				\State $\eta_2[i] \gets \eta_2[i] + 1$  \label{shims:eta2}
				\State $e^k_{ij} \gets E[i][\eta_2[i]]$
				\State $pv[i] \gets pv[i] + t^k_j.v$
			\Until{($\eta_2[i] = n_k$) {\bf or} ($ pv[i] \geq (1 + 3*gap)*p_i.v)$)} \label{shims:phase1b}

@@

\begin{table}[H]
\centering
\caption{Methods and scenarios with $1.2 \times volume$}  \label{tab:20}
\footnotesize
%\scriptsize
\begin{tabular}{rccccccccc}
\toprule
                                &{\bf Volume}         &                  &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
\cmidrule{4-9}		
{$method$}                      &{\bf surplus}        &{\bf Results}     &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&{\bf Speed-up} \\
\toprule
\multirow{6}{*}{\it {mpShims}} &\multirow{2}{*}{$1.2$}& $f$              & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  &   \\
                               &                      &{\bf run-time (s)}& 1     & 3     & 7     & 26    & 97    & 267   &   \\
\cmidrule{2-10}                               
                               &\multirow{2}{*}{$1.5$}& $f$              & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  &\\
                               &                      &{\bf run-time (s)}& 1     & 5     & 12    & 45    & 244   & 737   &\\
\cmidrule{2-10}                                 
                               &\multirow{2}{*}{$2.0$}& $f$              &&&&&&&\\
                               &                      &{\bf run-time (s)}&&&&&&&\\
\midrule

>>>>

\begin{algorithm}[H]
	\caption{$ACLP+RPDP (scenario,volume)$}  \label{alg:main}
	\begin{algorithmic}[1]
		\State Let $L, M, C$ be according to $scenario$ \label{main:LMC}
		\State $N \gets ItemsGeneration(scenario,volume)$ \label{main:items}
		\For {each $method$}

			\State $numProcs \gets $, the number of parallel processes to be used

			\For {each $\pi \in S_K$} \label{main:loop1}
				\State $f_{\pi} \gets SolveTour(\pi, L, M, C, N, method, numProcs )$ \label{main:method}
			\EndFor \label{main:loop2}
			\State $answer[scenario,volume,method] \gets \max f$ \label{main:f}
		\EndFor
		\State $ {\bf return}\ answer$
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{$SolveTour(\pi, L, M, C, N, method, numProcs)$}  \label{alg:tour}

@@

		\State $\pi(0) \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q_{\pi(k)}, E^Q_{\pi(k)}, M \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M \cup N_{\pi(k)} \cup Q_{\pi(k)}, E^Q_{\pi(k)})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M \gets SetPalletsDestination( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1, numProcs)$ \label{tour:node}
			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_2)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\State $ {\bf return}\ score / cost$ \label{tour:f}

@@

	\caption{ $SolveNode(mpACO, k, G, numProcs)$ } \label{alg:aco}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$
		\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets Greedy(k, G, 1)$  \label{aco:greedy}
		\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^*(V_k,E^{N*}_k \cup E^Q_k)$
		\State $A \gets$ a number of ants or parallel processes to be determined for each iteration \label{aco:ants}
		\State $ga^k_{ij}   \gets 0$, $1 \leq i \leq m$, $1 \leq j \leq n_k$  \label{aco:init1}
		\State $\tau^k_{ij} \gets 1$, $1 \leq i \leq m$, $1 \leq j \leq n_k$   \label{aco:init2}
		\State $\alpha    \gets 1.0$ \label{aco:alpha}
		\State $\beta     \gets 4.0$ \label{aco:beta}
		\State $\rho      \gets 0.2$ \label{aco:rho}
		\State $stagnant \gets 0$
		\While{($stagnant < 3$) {\bf and} ($runtime < 0.7s$)} \label{aco:while}

@@

Figure \ref{fig:whip} represents the $n_k$\/ possible edges $e_{ij}^k$\/ of $p_i$\/ sorted by $\theta_{ij}^k$. \emph{mpShims}\/ starts with a greedy solution, stopping at the edge with index $\eta_1[i]$ close to the local optimum (first phase). Then, considering even the edge with the index $\eta_2[i]$, it elaborates different possible complements for this pallet (second phase) and selects the best of these complements (third phase).

\begin{algorithm}[H]
	\caption{ $SolveNode(mpShims, k, G, numProcs)$}  \label{alg:shims}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$
		\State Sort $M$ by $|p_i.d|$ in non-descending order \label{shims:pallets}
		\State $E^N_k \gets \varnothing$ 
		\State Let $E[1..m][1..n_k]$, where $E[i]$ is an array with $n_k$ edges $(p_i,t^k_j)$ sorted by $\theta_{ij}^k$ in non-ascending order, $1 \leq i \leq m$ \label{shims:edges}

		\State $limits \gets getLimits(0.75,\ 0.98,\ numProcs)$, a list of unique limits, 1 for each process, between 0.75 and 0.98

		\For{$i \gets 1$ to $m$} 
			\State $pv[i] \gets 0$		\label{shims:phase1a}
			\State $\eta_1[i] \gets 0$
			\While{($p_i.v - pv[i] > gap*p_i.v$) {\bf and} ($\eta_1[i]<n_k$)} \label{shims1:slack}
				\State $\eta_1[i] \gets \eta_1[i] + 1$ \label{shims:eta1}
				\State $e^k_{ij} \gets E[i][\eta_1[i]]$
				\If{($e^k_{ij}$ is feasible) {\bf and} ($t^k_j.v \leq p_i.v - pv[i]$)} 
					\State $E^N_k \gets E^N_k \cup \{e^k_{ij}\}$
					\State $pv[i] \gets pv[i] + t^k_j.v$ 
				\EndIf
			\EndWhile 
			\State $slack[i] \gets p_i.v - pv[i]$
			\State $\eta_2[i] \gets \eta_1[i]$
			\Repeat
				\State $\eta_2[i] \gets \eta_2[i] + 1$  \label{shims:eta2}
				\State $e^k_{ij} \gets E[i][\eta_2[i]]$
				\State $pv[i] \gets pv[i] + t^k_j.v$
			\Until{($\eta_2[i] = n_k$) {\bf or} ($ pv[i] \geq (1 + 3*gap)*p_i.v)$)} \label{shims:phase1b}

@@

\begin{table}[H]
\centering
\caption{Methods and scenarios with $1.2 \times volume$}  \label{tab:20}
\footnotesize
%\scriptsize
\begin{tabular}{rccccccccc}
\toprule
                                &{\bf Volume}         &                  &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
\cmidrule{4-9}		
{$method$}                      &{\bf surplus}        &{\bf Results}     &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&{\bf Speed-up} \\
\toprule
\multirow{6}{*}{\it {mpShims}} &\multirow{2}{*}{$1.2$}& $f$              & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  &   \\
                               &                      &{\bf run-time (s)}& 1     & 3     & 7     & 26    & 97    & 267   &   \\
\cmidrule{2-10}                               
                               &\multirow{2}{*}{$1.5$}& $f$              & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  &\\
                               &                      &{\bf run-time (s)}& 1     & 5     & 12    & 45    & 244   & 737   &\\
\cmidrule{2-10}                                 
                               &\multirow{2}{*}{$2.0$}& $f$              & 11.31 & 6.29  & 5.54  & 5.83  & 5.05  & 10.63 &\\
                               &                      &{\bf run-time (s)}& 2     & 14    & 34    & 106   & 477   & 2417  &\\
\midrule
